Spontaneous Similarity Judgments of Musical Tones played with various Playing Techniques

### 2017-12-14 paper/lagrangeSpontaneousSimilarity2017.tex
better figures

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/groupModes.png}
\caption{Clustering \ipt using average perceptual similarity into 5 clusters (top) and playing technique labels (top). The color chosen to display each clusters on top corresponds to the playing technique that is dominant in this cluster.\ml{change colormap}}
\label{fig:gm}
\end{figure}

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/groupInstruments.png}
\caption{Clustering \ipt using average perceptual similarity into 8 clusters (a) and instrument reference labels (b). The color chosen to display the groups (on top) corresponds  to the instrument that is dominant in this group.}
\label{fig:gi}
\end{figure}

@@

Those instruments are recorded for different nuance and pitch if the latter is relevant, but more importantly, several playing technique are considered. For  the second experiment described in this paper, the playing techniques considered are: artificial-harmonic (art), blow (blow), exploding slap  (explo), harmonic (harm), key-click (key), col legno   (legno), non vibrato (nonvib), ordinario (ord), pedal tone (pdl), pizzicato (pizz), ponticello (pont), slap (slap), (tasto), tongue-ram (tng), and xylophonic (xyl).

@@

\begin{figure}
\center
%\includegraphics[width = \textwidth]{figures/dendrogram.pdf}
\caption{Dendrogram obtained after processing the similarity judgment matrix using the agglomerative clustering algorithm.}
\label{fig:dendrogram}
\end{figure}

>>>>

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/groupModes.png}
\caption{Clustering \ipt using average perceptual similarity into 5 clusters (top) and playing technique labels (top). The color chosen to display each clusters on top corresponds to the playing technique that is dominant in this cluster, from left to right: 'pizzicato', 'slap', 'key', 'ordinario', 'ordinario', 'ponticello', 'art'.}
\label{fig:gm}
\end{figure}

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/groupInstruments.png}
\caption{Clustering \ipt using average perceptual similarity into 8 clusters (a) and instrument reference labels (b). The color chosen to display the groups (on top) corresponds  to the instrument that is dominant in this group, from left to right: 'ASax', 'BBTb', 'Vc', 'ASax', 'TpC', 'Gtr', 'ASax', 'Vc'.}
\label{fig:gi}
\end{figure}

@@

Those instruments are recorded for different nuance and pitch if the latter is relevant, but more importantly, several playing technique are considered. For  the second experiment described in this paper, the playing techniques considered are: artificial harmonic (art), blow (blow), exploding slap  (explo), harmonic (harm), key-click (key), col legno   (legno), non vibrato (nonvib), ordinario (ord), pedal tone (pdl), pizzicato (pizz), ponticello (pont), slap (slap), (tasto), tongue-ram (tng), and xylophonic (xyl).

@@

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/dendrogram.pdf}
\caption{Dendrogram obtained after processing the similarity judgment matrix using the agglomerative clustering algorithm.}
\label{fig:dendrogram}
\end{figure}
